CLT item selection

### 2022-04-28 analysis/clt_item_selection.Rmd
update item selections
update item selection algo

all_model_params <- read_csv("../data/model_parameters_3PL.csv")
```

@@

```{r}
# exclude items based on differential item functioning

exclude <- c("choir", "flounder", "badger")

model_params <- all_model_params%>%
  filter(!item %in% exclude)
```

@@

full <- data%>%
  group_by(subjID)%>%
  summarise(mean_full = mean(correct))

score_fn <- function(subset) {
	easinesses <- sort(easiness[subset])
	nn_dists <- rep(0, sum(subset)-1)
	for(i in 1:sum(subset)-1) {
		nn_dists[i] <- easinesses[i+1] - easinesses[i]
	}
	spacing <- -1*sd(nn_dists)
	mean_discrim <- mean(discrimination[subset])
	mean_spread <- mean(easy_spread[subset])

@@

for (i in 5:45) {

>>>>

all_model_params <- read_csv("../data/model_parameters_3PL.csv")

params_sex <- readRDS("../saves/model_params_irt3_dif_sex.rds")%>%
  select(-uci, -lci)%>%
  pivot_wider(names_from = sex, values_from = mode)%>%
  mutate(sex_dif = f-m)

params_order <- readRDS("../saves/model_params_irt3_dif_order.rds")%>%
  select(-uci, -lci)%>%
  pivot_wider(names_from = order, values_from = mode)%>%
  mutate(order_dif = A-B)
```

@@

```{r}
# exclude items based on differential item functioning
## Split by sex
params_sex_p <- params_sex%>%
  group_by(nlpar)%>%
  mutate(sd = sd(sex_dif), 
         cut_low = mean(sex_dif)-2*sd,
         cut_high = mean(sex_dif)+2*sd)

ggplot(params_sex_p, aes(x = sex_dif))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_histogram(col = "black", alpha = .5)+
  facet_grid(~nlpar)+
  theme_minimal()

ggplot(params_sex_p, aes(x = sex_dif, label = item, y = reorder(item, abs(sex_dif))))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_point(col = "black", alpha = .5)+
  facet_grid(~nlpar)+
  theme_minimal()

exclude_sex <- params_sex_p%>%
  filter(sex_dif < cut_low | sex_dif > cut_high)%>%
  pull(item)

## Split by Order

params_order_p <- params_order%>%
  group_by(nlpar)%>%
  mutate(sd = sd(order_dif), 
         cut_low = mean(order_dif)-2*sd,
         cut_high = mean(order_dif)+2*sd)

ggplot(params_order_p, aes(x = order_dif))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_histogram(col = "black", alpha = .5)+
  facet_grid(~nlpar)+
  theme_minimal()

ggplot(params_order_p, aes(x = order_dif, label = item, y = reorder(item, abs(order_dif))))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_point(col = "black", alpha = .5)+
  facet_grid(~nlpar)+
  theme_minimal()

exclude_order <- params_order_p%>%
  filter(order_dif < cut_low | order_dif > cut_high)%>%
  pull(item)

model_params <- all_model_params%>%
  filter(!item %in% exclude_sex,
         !item %in% exclude_order)
```

full <- data%>%
  group_by(subjID)%>%
  summarise(mean_full = mean(correct))
```

@@

```{r}
score_fn <- function(subset) {
	easinesses <- sort(easiness[subset])
	nn_dists <- rep(0, sum(subset)-1)
	for(i in 1:sum(subset)-1) {
		nn_dists[i] <- easinesses[i+1] - easinesses[i]
	}
	spacing <- -1*sd(nn_dists)
	mean_discrim <- mean(discrimination[subset])
	mean_spread <- mean(easy_spread[subset])

@@

for (i in 5:40) {
